EuPPollNet: A European database of plant-pollinator networks

### 2024-04-05 Manuscript/Ms.qmd
minor edits

The EuPPollNet database is available in both .csv and .rds formats. The .csv file contains data in long format, while the .rds file stores the data in a list structure, with networks organized within each study. The data is organized in three different files named interaction data, flower count data and metadata. The interaction file contains `r nrow(my_tibble) + 1` columns that depict where and when the plant-pollinator interaction was observed (**Table 1**). To provide a standard unit of plant-pollinator interaction across studies, each row depicts a single interaction between a plant and a pollinator species. To build a plant-pollinator network matrix at a site level, authors only need to group interactions by plant and pollinator species, site and study. In addition, information about habitat type and bioclimatic region are also provided in this file. The floral count file contains measurements of floral availability and the unit of measurement, and should be merged with the interaction file by using the column of "Floral_data_merger. Only xxxx% of studies contain floral count information. The metadata file contains [...]

>>>>

The EuPPollNet database is available in both .csv and .rds formats. The .csv file contains data in long format, while the .rds file stores the data in a list structure, with networks organized within each study. The data is organized in three different files named interaction data, flower count data and metadata. The interaction file contains `r nrow(my_tibble) + 1` columns that depict where and when the plant-pollinator interaction was observed (**Table 1**). To provide a standard unit of plant-pollinator interaction across studies, each row depicts a single interaction between a plant and a pollinator species. To build a plant-pollinator network matrix at a site level, authors only need to group interactions by plant and pollinator species, site and study. In addition, information about habitat type and bioclimatic region are also provided in this file. The floral count file contains measurements of floral availability and the unit of measurement, and should be merged with the interaction file by using the column of "Flower_data_merger". Only xxxx% of studies contain floral count information. The metadata file contains [...]
